---
title: "Gender Data Report"
output: 
    html_document:
        toc: true
---


``` {r, include=FALSE, echo=FALSE}
library(plyr)
library(dplyr)
library(ggplot2)
library(lubridate)
library(knitr)

pg_conf <- read.csv('rds_settings', stringsAsFactors=FALSE)
vs_db <- src_postgres(dbname='vitalsigns', host=pg_conf$host,
                      user=pg_conf$user, password=pg_conf$pass,
                      port=pg_conf$port)

hh_sec_b <- tbl(vs_db, build_sql('SELECT * FROM "curation__household_secB"')) %>%
  data.frame

hh_sec_c <- tbl(vs_db, build_sql('SELECT * FROM "curation__household_secC"')) %>%
  data.frame

hh_sec_e <- tbl(vs_db, build_sql('SELECT * FROM "curation__household_secE"')) %>%
  data.frame

hh_sec_hv1 <- tbl(vs_db, build_sql('SELECT * FROM "curation__household_secHV1"')) %>%
  data.frame

hh_all <- 
  merge(hh_sec_b, hh_sec_c, by=c("Household.ID", "Individual.ID", "Landscape..", "Country")) %>%
  select(Country, Landscape.., Household.ID, Individual.ID, hh_b02, hh_b04, hh_c02, hh_c03, hh_c07) %>%
  
  merge(hh_sec_e, by=c("Household.ID", "Individual.ID", "Landscape..", "Country")) %>%
  select(Country, Landscape.., Household.ID, Individual.ID, hh_b02, hh_b04, hh_c02, hh_c03, hh_c07, hh_e04, hh_e25, hh_e24_1, hh_e24_2, hh_e52, hh_e06, hh_e65_1, hh_e65_2) %>%
  
  merge(hh_sec_hv1, by=c("Household.ID", "Individual.ID", "Landscape..", "Country")) %>%
  select(Country, Landscape.., Household.ID, Individual.ID, hh_b02, hh_b04, hh_c02, hh_c03, hh_c07, hh_e04, hh_e25, hh_e24_1, hh_e24_2, hh_e52, hh_e06, hh_e65_1, hh_e65_2, hh_hv103, hh_hv104, hh_hv105, hh_hv105_unit, hh_hv105a) %>%
  
  data.frame

hh_all$Gender <- revalue(hh_all$hh_b02, c(`1`='Male', `2`='Female'))

```

Report generated `r now(tzone='UTC')` UTC.     
Note: Vital Signs uses a hierarchical, targeted sampling methodology, and statistics may not be nationally representative.

#Education
## Literacy
Can [NAME] read or write? (In English or Local Languages)      
*n=(`r nrow(hh_all[!is.na(hh_all$hh_c02), ])`)*
``` {r, fig.align="center", echo=FALSE, warning=FALSE}

hh_all$hh_c02 <- revalue(hh_all$hh_c02, c(`1`=1, `2`=1, `3`=1, `4`=1, `5`=0)) %>% as.numeric

data <- hh_all %>% group_by(Country, Gender) %>% summarize(`Literacy Rate`=mean(hh_c02, na.rm=T)) %>% data.frame

kable(data)

ggplot(data) +
    geom_bar(aes(Country, Literacy.Rate, fill=Gender), stat='identity', position='dodge')
```


## School Attendence Rate
Has [NAME] ever attended school?       
*n=(`r nrow(hh_all[!is.na(hh_all$hh_c03), ])`)*
``` {r, fig.align="center", echo=FALSE, warning=FALSE}

hh_all$hh_c03 <- revalue(hh_all$hh_c03, c(`1`=1, `2`=0)) %>% as.numeric

data <- hh_all %>% group_by(Country, Gender) %>% summarize(Percent.Attended.School=mean(hh_c03, na.rm=T)) %>% data.frame

kable(data)

ggplot(data) +
    geom_bar(aes(Country, Percent.Attended.School, fill=Gender), stat='identity', position='dodge')
```

<!---It's impossible to recode all of the different education vars!
Maybe we should look at how they map together
## Higest Grade Completed
``` {r, fig.align="center"}
#hh_all$hh_c07 <- hh_all$hh_c07 %>% as.numeric
#hh_all$Highest.Grade.Completed <- hh_all$hh_c07 %>% as.numeric

#data <- hh_all %>% group_by(Country, Gender) %>% summarize(Highest.Grade.Completed=mean(hh_c07, na.rm=T)) %>% data.frame

#kable(data)

#hh_sel <- hh_all[

#ggplot(hh_all) +
    #geom_density(aes(Highest.Grade.Completed, fill=Gender), alpha=0.8) + facet_wrap(~Country)
```
--->


#Labor
## Worked in the past week
Did you do any work for any type of pay, profit, barter or home use during the last 7 days? (includes farm activites)    
*n=(`r nrow(hh_all[!is.na(hh_all$hh_e04), ])`)*
``` {r, fig.align="center", echo=FALSE, warning=FALSE}

hh_all$hh_e04 <- revalue(hh_all$hh_e04, c(`1`=1, `2`=0)) %>% as.numeric

data <- hh_all %>% group_by(Country, Gender) %>% summarize(Percent.Worked.Recently=mean(hh_e04, na.rm=T)) %>% data.frame

kable(data)

ggplot(data) +
    geom_bar(aes(Country, Percent.Worked.Recently, fill=Gender), stat='identity', position='dodge')
```


## Hours Worked In Previous Week
How many hours did you work last week?  
*n=(`r nrow(hh_all[!is.na(hh_all$hh_e25), ])`)*
``` {r, fig.align="center", echo=FALSE, warning=FALSE}
hh_all$Hours.Worked.Last.Week <- hh_all$hh_e25

data <- hh_all %>% group_by(Country, Gender) %>% summarize(Mean.Hours.Worked.Last.Week=mean(hh_e25, na.rm=T)) %>% data.frame

kable(data)

ggplot(data) +
    geom_bar(aes(Country, Mean.Hours.Worked.Last.Week, fill=Gender), stat='identity', position='dodge')

ggplot(hh_all) +
    geom_boxplot(aes(Country, Hours.Worked.Last.Week, fill=Gender))
```


## Businesses
Did you operate any business or do any self-employed activity during the last 12 months, other than agriculture?  
*n=(`r nrow(hh_all[!is.na(hh_all$hh_e52), ])`)*
``` {r, fig.align="center", echo=FALSE, warning=FALSE}

hh_all$hh_e52 <- revalue(hh_all$hh_e52, c(`1`=1, `2`=0)) %>% as.numeric

data <- hh_all %>% group_by(Country, Gender) %>% summarize(Percent.Operated.Business=mean(hh_e52, na.rm=T)) %>% data.frame

kable(data)

ggplot(data) +
    geom_bar(aes(Country, Percent.Operated.Business, fill=Gender), stat='identity', position='dodge')
```


## Other Economic Activities
On which economic activity do you spend most of your time?  
*n=(`r nrow(hh_all[!is.na(hh_all$hh_e06), ])`)*
``` {r, fig.align="center", echo=FALSE, warning=FALSE}

hh_all$Main.Economic.Activity <- revalue(hh_all$hh_e06, c(`1`='Paid Employee', `2`='Self Employed (With Employees)', `3`='Self Employed (Without Employees)', `4`='Unpaid Family Helper (Agriculture)', `5`='Unpaid Family Helper (Non-Agriculture)', `6`='On Your Own Farm')) %>% as.character

data <- hh_all %>% filter(!is.na(Main.Economic.Activity)) %>%
  group_by(Country, Main.Economic.Activity, Gender) %>% 
  summarize(n=n()) %>% mutate(Percent=n/sum(n)) %>% 
  select(Country, Main.Economic.Activity, Gender, Percent) %>% 
  data.frame

kable(data)

ggplot(data) +
  geom_bar(aes(Main.Economic.Activity, Percent, fill=Gender), stat='identity', position='dodge') +
  facet_wrap(~Country) + 
  theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5))
```


## Net Income
What was your net income (profit) from your business or businesses in the last month?  
*To scale for differences in currencies, statistics calculated as percent of recorded income at the national level.*  
*n=(`r nrow(hh_all[!is.na(hh_all$hh_e65_1), ])`)*
``` {r, fig.align="center", echo=FALSE, warning=FALSE}
hh_all$Net.Income <- hh_all$hh_e65_1

data <- filter(hh_all, !is.na(hh_e65_1))

data$Net.Income[data$Net.Income=="week"] <- data$Net.Income[data$Net.Income=="week"]*(31/7)

country_income <- data %>% group_by(Country) %>% 
  summarize(n=sum(Net.Income)) 

percent_income <- merge(data, country_income, by=c('Country'))
percent_income$Percent.National.Net.Income <- percent_income$Net.Income/percent_income$n

data <- percent_income %>% group_by(Country, Gender) %>% summarize(Percent.National.Net.Income=sum(Percent.National.Net.Income))

kable(data)

ggplot(data) +
  geom_bar(aes(Country, Percent.National.Net.Income, fill=Gender), stat='identity', position='dodge')

```


#Fuelwood
## Who collects?
Does [NAME] collect fuelwood for household and/or commercial use?  
*n=(`r nrow(hh_all[!is.na(hh_all$hh_hv103), ])`)*
``` {r, fig.align="center", echo=FALSE, warning=FALSE}

hh_all$hh_hv103 <- revalue(hh_all$hh_hv103, c(`1`=1, `2`=0)) %>% as.numeric

data <- hh_all %>% group_by(Country, Gender) %>% summarize(Percent.Collects.Firewood=mean(hh_hv103, na.rm=T)) %>% data.frame

kable(data)

ggplot(data) +
    geom_bar(aes(Country, Percent.Collects.Firewood, fill=Gender), stat='identity', position='dodge')
```


## Frequency
How frequently does [NAME] collect firewood?  
*n=(`r nrow(hh_all[!is.na(hh_all$hh_hv104), ])`)*
``` {r, fig.align="center", echo=FALSE, warning=FALSE}
hh_all$Frequency <- revalue(hh_all$hh_hv104, c(`1`='Weekly', `2`='Monthly', `3`='Seasonally', `4`='Annually')) %>% as.character

data <- hh_all %>% filter(!is.na(Frequency)) %>%
  group_by(Country, Gender, Frequency) %>% 
  summarize(n=n()) %>% mutate(Percent=n/sum(n)) %>% 
  select(Country, Gender, Frequency, Percent) %>% 
  data.frame

kable(data)

ggplot(data) +
  geom_bar(aes(Frequency, Percent, fill=Gender), stat='identity', position='dodge') +
  facet_wrap(~Country) + 
  theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5))
```


## Hours Spent Collecting Fuelwood
How many hours does [NAME] spend on each fuelwood collection trip? (From home departure to return)  
*n=(`r nrow(hh_all[!is.na(hh_all$hh_hv105a), ])`)*
``` {r, fig.align="center", echo=FALSE, warning=FALSE}
hh_all$Hours.Spent <- hh_all$hh_hv105a

data <- hh_all %>% group_by(Country, Gender) %>% summarize(Mean.Hours.Spent=mean(Hours.Spent, na.rm=T)) %>% data.frame

kable(data)

ggplot(hh_all[which(hh_all$Hours.Spent < 10), ]) + geom_boxplot(aes(Country, Hours.Spent, fill=Gender))
```
